Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-04 paper/galsize_paper.tex
Cleaned up and shortened results sections - now moved most of the interpretation to the following section

In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for several different kinds of empirical models, described in turn below.

@@

{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all. APH: The big picture being compared/tested here are ``pre-infall" vs. ``post-infall" processes, respectively. Those don't seem like great names either though.}

@@

\subsection{Failure of $\mstar-$based Models}
\label{subsec:mstar_stripping}

The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the $\mstar-$based model described in \S\ref{subsubsec:mstaronlymodel}. In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ even though the observed one-point distributions are recovered exactly.

The reason for the null signal of the purely $\mstar-$based model is simply that the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property. This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as subhalo assembly. The purely $\mstar-$based model gives us a useful starting point to test simple alternative hypotheses for how the scatter may be correlated with large-scale structure. This is the motivation behind the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}. In this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping, where the amount of stripping has been calibrated to the satellite mass loss seen in high-resolution hydrodynamical simulations.

The treatment of stellar mass loss in this model naturally results in an enhancement of size differences between satellites and centrals. As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, these central/satellite differences impact $\rhalf-$dependent clustering in the expected manner: small galaxies cluster more strongly relative to large galaxies of the same stellar mass. Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds. This confirms the notion that central vs. satellite differences drive the $\rhalf-$dependence of clustering, although the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS. It is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations. Taken together with the results for the $\rvir-$based model presented in \S\ref{subsec:clustering_results} and shown in Figure \ref{fig:clustering_ratio_upshot}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall. We discuss the physical implications of this result in \S\ref{sec:interpretation}.

@@

>>>>

In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for several different kinds of empirical models, described in turn below.
{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all. APH: The big picture being compared/tested here are ``pre-infall" vs. ``post-infall" processes, respectively. Those don't seem like great names either though.}

@@

@@

\subsection{Testing the Impact of Satellite Mass Loss}
\label{subsec:mstar_stripping}

The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the $\mstar-$based model described in \S\ref{subsubsec:mstaronlymodel}. In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property. This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as halo assembly. Likewise, the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel} also exhibits correlations between scatter in $\rhalf$ and halo properties: in this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.

The treatment of stellar mass loss in this model naturally results in an enhancement of size differences between satellites and centrals. As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, this impacts $\rhalf-$dependent clustering in the expected manner. The ``small" galaxy population has a higher satellite fraction, and so in this model small galaxies cluster more strongly relative to large galaxies of the same stellar mass. However, the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS. Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations. As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.

@@

{\color{blue} Important point/sentence to reincorporate here, after deleting from above:} Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds. {\color{blue} The analogous point should be made when discussing the role of color/morphology selection}.
